The effect of genetic linkage on island endemics richness

### 2018-08-24 paper/draft.tex
some disc

\begin{figure}
  %\includegraphics{}
  \caption{[2 x 3]
    Exemplary genealogies of lineages in isolation for different degrees of genetic linkage.
    extant individuals.
    Columns: phylogeny and genealogy
    Rows: Lineage with low gene linkage,
    lineage with intermediate gene linkage,
    lineage with high gene linkage.}
  \label{phylogenies}
\end{figure}

@@

@@

In this work we concentrated on genetic influences on speciation.
However, there is ongoing debate on how strongly genetic factors also impact extinction processes (Jamieson 2007).
For example, [discuss the evolutionary rescue studied by Schiffers et al. 2013]
Seeing that observed speciation rates are in fact net speciation rates highlights the need to mechanistically explore
these processes as well.
In fact, genetic processes might play an important role in the issue of extinction debt. %% cite Ludmilla, ask for refs

>>>>

\begin{figure}
  %\includegraphics{}
  \caption{[2 x 3]
    Exemplary phylogenies of lineages in isolation for different degrees of genetic linkage over time.
    Rows: Lineage with low gene linkage,
    lineage with intermediate gene linkage,
    lineage with high gene linkage.}
  \label{phylogenies}
\end{figure}

@@

Besides patterns of species and genetic diversity, our model is able to produce all relevant data for
numerous analyses like rank-abundance, species-area-relations, $\alpha$-, $\beta$-, $\gamma$-diversity etc.
This creates additional possibilities of comparing, validating and calibrating the model to real world patterns \cite{SimpleModelsLead2013}. % other paper? -> check mech. isl. mods-review

@@

In this work we concentrated on genetic influences on speciation.
However, there is ongoing debate on how strongly genetic factors also impact extinction processes (Jamieson 2007).
For example, [discuss the evolutionary rescue studied by Schiffers et al. 2013]
Seeing that observed speciation rates are in fact net speciation rates highlights the need to mechanistically explore
these processes as well.
In fact, genetic processes might play an important role in the issue of extinction debt. %% cite Ludmilla
